Multi-line Intensity Mapping

### 2019-06-14 paper/ms.tex
Add k, mu Fisher matrix

\subsection{Interloping Lines} \label{ssec:interlopers}
The multi-field method relies only on the measurements of cross-spectra beween
various lines. Interloping lines do not contribute to the average
cross-spectra signal, but does contribute to the noise of the measurement. We
can account for this by modifying the equation for $N_i$ to be
\citep{2016ApJ...825..143L, 2016ApJ...832..165C},
\beq\label{eq:ptot_intlpr}
N_i = N_{i,\text{instrumental}} + \sum_{j} \frac{1}{\apar(z_j) \aperp(z_j)^2} 
            P_j\left(\frac{\kpar}{\apar(z_j)}, 
                     \frac{\kperp}{\aperp(z_j)}\right)\text{,}
\eeq
where $N_{i,\text{instrumental}}$ is the instrumental noise of line $i$ at the
observed frequency, the sum on $j$ is over all interloping lines, $z_j$ is the
emitted redshift of line $j$, and where,
\begin{alignat}{2}
\apar = \frac{H(z_i)}{H(z_j)} \frac{1+z_j}{1+z_i} \quad \quad &&
\aperp = \frac{D_{A}(z_j)}{D_A(z_i)}\text{,}
\end{alignat}
where $z_i$ is the emitted redshift of line $i$ and $D_A(z)$ is the comoving
angular diameter distance to redshift $z$.

For simplicity, we assume the instrumental noise is white (i.e.
$N_{i,\text{instrumental}}$ is constant).

>>>>

\subsection{Interloping Lines} \label{ssec:interlopers}
The multi-field method relies only on the measurements of cross-spectra beween
various lines. Interloping lines do not contribute to the average
cross-spectra signal, but does contribute to the noise of the measurement. We
can account for this by modifying the equation for $N_i$ to be
\citep{2016ApJ...825..143L, 2016ApJ...832..165C},
\beq\label{eq:ptot_intlpr}
N_i = N_{i,\text{instrumental}} + \sum_{j} \frac{1}{\apar(z_j) \aperp(z_j)^2} 
            P_j\left(\frac{\kpar}{\apar(z_j)}, 
                     \frac{\kperp}{\aperp(z_j)}\right)\text{,}
\eeq
where $N_{i,\text{instrumental}}$ is the instrumental noise of line $i$ at the
observed frequency, the sum on $j$ is over all interloping lines, $z_j$ is the
emitted redshift of line $j$, and where,
\begin{alignat}{2}
\apar = \frac{H(z_i)}{H(z_j)} \frac{1+z_j}{1+z_i} \quad \quad &&
\aperp = \frac{D_{A}(z_j)}{D_A(z_i)}\text{,}
\end{alignat}
where $z_i$ is the emitted redshift of line $i$ and $D_A(z)$ is the comoving
angular diameter distance to redshift $z$. For simplicity, we assume the
instrumental noise is white (i.e. $N_{i,\text{instrumental}}$ is constant),
though it is straightforward in this formalism to incorporate a $k$- or
$\mu$-dependence in the instrumental noise.

Unlike in the three field case, where the integrand of the Fisher matrix was
only dependent on $k$, the noise and therefore covariance matrix depends also
on $\mu$. Galactic foregrounds can imprint an azimuthal dependence as well,
which we do not consider in this work. Incorporating a polar dependence is straightforward, and we can write the Fisher matrix as:
\beq\label{eq:fisher_mu}
F_{i,j} = 
\int \frac{\text{d}k\,\text{d}\mu}{(2\pi)^2} k^2 V_{\text{surv}}
% \int \frac{\text{d}k\,k^2}{2\pi^2} V_{\text{surv}} 
\sum_{l} \sum_{m}
\frac{\partial \hat{P}_{l}(k, \mu)}{\partial B_i}
\left(\Cov{\hat{P}_{l}(k, \mu)}{\hat{P}_{m}(k, \mu)}\right)^{-1}
\frac{\partial \hat{P}_{m}(k, \mu)}{\partial B_j}\text{,}
\eeq
